\LARGE \bf Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty [v7 Feb 18, 2015 ]

### 2015-03-11 paper.tex
Changed the figures to scales

\begin{figure}%
    \centering
     \subfloat{{\includegraphics[width=8.5cm, height=7cm]{matlab_figures/pfc.eps} }}%

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height = 9cm]{matlab_figures/pfc.eps}
\caption{ \footnotesize Comparison of the current average probability of force closure vs. the stopping time $T_s$.Graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.  We demonstrate this for Thompson, Gittins, Monte-Carlo and the Adaptive Sampling approach \cite{kehoe2012toward}. We also demonstrate what the average probability of force closure for the approximate optimal policy. Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
\vspace*{-10pt}
\label{fig:grasp_quality}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width = 9cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Monte-Carlo, Thompson, Gittins). Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object. The best grasps are ranked 1 and worst are 1000. As illustrated the MAB algorithms intelligently allocate samples towards high quality grasps based on past observations, where Monte-Carlo Integration takes a uniform approach to allocation. }

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 9cm, height = 9cm]{matlab_figures/confidence_bounds.eps}
\caption{ \footnotesize \todo{We might want to condense Fig 6 and Fig. 4. The confidence intervals clutter the plot though} The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, the adaptive sampling method and Monte-Carlo sampling. Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object. The sharper decrease in confidence interval corresponds to more samples being allocated for the return grasp. }

@@

\begin{figure}[ht!]
\centering
\includegraphics[width = 8cm, height = 9cm]{matlab_figures/worst_case.eps}
\caption{ \footnotesize Comparison of the current average probability of force closure vs. the stopping time $T_s$ for the pathological case where the samples are sorted to be misleading. The graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.  We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}. We also demonstrate what the average probability of force closure for the approximate optimal policy. Empirically, it appears that when samples are misleading the best policy is uniform allocation. However, it also illustrated that Thompson sampling can recover from this situation where Gittins and Kehoe et al.  are not able to and get stuck in local solutions. }
\vspace*{-10pt}
\label{fig:worst_case}
\end{figure}

>>>>

\begin{figure}%
    \centering
     \subfloat{{\includegraphics[scale=0.25]{matlab_figures/pfc.eps} }}%

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.25]{matlab_figures/pfc.eps}
\caption{ \footnotesize Comparison of the current average probability of force closure vs. the stopping time $T_s$.Graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.  We demonstrate this for Thompson, Gittins, Monte-Carlo and the Adaptive Sampling approach \cite{kehoe2012toward}. We also demonstrate what the average probability of force closure for the approximate optimal policy. Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
\vspace*{-10pt}
\label{fig:grasp_quality}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.25]{matlab_figures/pulls_per_grasp.eps}
\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Monte-Carlo, Thompson, Gittins). Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object. The best grasps are ranked 1 and worst are 1000. As illustrated the MAB algorithms intelligently allocate samples towards high quality grasps based on past observations, where Monte-Carlo Integration takes a uniform approach to allocation. }

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.25]{matlab_figures/confidence_bounds.eps}
\caption{ \footnotesize \todo{We might want to condense Fig 6 and Fig. 4. The confidence intervals clutter the plot though} The probability of Force Closure of the grasp returned vs the number of samples required with a $95\%$ confidence interval around the return value for Thompson Sampling, the adaptive sampling method and Monte-Carlo sampling. Graph is averaged over 100 objects from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each object. The sharper decrease in confidence interval corresponds to more samples being allocated for the return grasp. }

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.25]{matlab_figures/worst_case.eps}
\caption{ \footnotesize Comparison of the current average probability of force closure vs. the stopping time $T_s$ for the pathological case where the samples are sorted to be misleading. The graph is averaged over 100 objects randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each object.  We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}. We also demonstrate what the average probability of force closure for the approximate optimal policy. Empirically, it appears that when samples are misleading the best policy is uniform allocation. However, it also illustrated that Thompson sampling can recover from this situation where Gittins and Kehoe et al.  are not able to and get stuck in local solutions. }
\vspace*{-10pt}
\label{fig:worst_case}
\end{figure}
